---
title: "Homework 5"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

**Read in the homicide dataset**

```{r, message = FALSE}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

The raw dataset shows us information on homicides in 50 U.S. cities; it contains variables such as id, city/state and latitude and longitude for the location of the murder, date of reported crime, and information about the victim such as name, race, age, and sex.

We created a city_state variable and are looking at each case based on whether or not they are solved/unsolved.

**Looking at the dataset**

```{r, aggregate, message = FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

In this step we are summarizing to obtain number of unsolved and total homicides in each city_state.

**Proportion test for Baltimore, MD:**

```{r, prop.test, collapse = TRUE}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

**Iterate the proportion test for each city:**

```{r, results_df}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

**Plot:**

```{r, results_df plot}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

**Read in all datasets and create tidy dataframe**

```{r, path_df, message = FALSE}
path_df = 
  tibble(
    path = list.files("data/study")
  ) %>% 
  mutate(
    path = str_c("data/study/", path),
    data = map(.x = path, ~read_csv(.x)) # reading in datasets
  ) %>% 
  unnest(data) %>% 
  mutate(
    path = str_replace(path, "data/study/", ""),
    id = path,
    id = str_replace(id, ".csv", ""),
  ) %>% # pivot longer to tidy data
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observation",
    names_prefix = "week_"
  ) %>% 
  mutate(
    week = as.numeric(week)
  ) %>% 
  select(-path)
```

**Create spaghetti plot and comment on group differences**

```{r, path_df plot}
path_df %>% 
  ggplot(aes(x = week, y = observation, color = id)) +
  geom_line()
```

From the plot we can see that the control observation values are lower than the experimental group's observations. Additionally, while the control group's values seem to be stable over the 8 weeks, the experimental group's values seem to be increasing.

## Problem 3

Function that will run a t.test to be used later and tibble with normal distribution with sample size of 30, standard deviation of 5 

```{r, sim_test}
sim_test = function(n = 30, mu, sigma = 5) {
  
  sim_data = 
    tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
    t.test() %>% 
    broom::tidy()
  
}
```

Running the simulation for mu = 0

```{r, sim_results}
sim_results = 
  rerun(5000, sim_test(30, 0, 5)) %>% 
  bind_rows()
```

Running simulation for mu = {0, 1, 2, 3, 4, 5, 6}

```{r, sim_results_means}
sim_results = 
  tibble(mu = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mu, ~rerun(5000, sim_test(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs) %>% 
  mutate(
    mu_hat = estimate
  ) %>% 
  select(-estimate) %>% 
  relocate(mu, mu_hat)
```



